Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-09-18 manuscript.Rmd

```{r summarySetUp, eval=TRUE}
unique.titles <- filter(full.df, attributes == "journal") %>%
  group_by(record) %>%
  summarise(N = n())

articles.titleMatching <- length(which(full.df$attributes == "article"))

journals.titleMatching <- filter(full.df, attributes == "journal") %>%
  summarise(Unique = n_distinct(record))

articles.otherDocuments <- length(which(full.df$attributes == "article"))

journals.otherDocuments <- filter(full.df, attributes == "journal") %>% 
  summarise(Unique = n_distinct(record))

articles.final <- length(which(full.df$attributes == "article"))

journals.final <- filter(full.df, attributes == "journal") %>% 
  summarise(Unique = n_distinct(record))

unique.titles <- filter(full.df, attributes == "journal") %>%
  group_by(record) %>%
  mutate(Hodge.list = ifelse(record %in% hodge == TRUE, 1, 0)) %>%
  summarise(N = n(), Hodge.list = max(Hodge.list)) %>%
  mutate(Hodge = ifelse(Hodge.list == 1, "Y", "N"))

n.so.yr <- filter(full.df, attributes == "journal" | attributes == "pubYear")

n.so <- filter(full.df, attributes == "journal") %>% mutate(title = record) %>% 
  select(-attributes, -record)

unique.titles
```

```{r Figure 1a - Journals, eval=FALSE}

#=======================================
# Journals
#=======================================

@@

figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + 
    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = exp.05, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = exp.04, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2016.5, y = 60, label = "Observed growth", size = 5) +
    annotate("text", x = 2016.5, y = 70, label = "Linear growth\n (slope=1.9)", size = 5) + 
    annotate("text", x = 2016, y = 76, label = "4% CAGR", size = 5) + 
    annotate("text", x = 2015.5, y = 95, label = "5% CAGR", size = 5) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19))

```{r Figure 1b - Journals, eval=FALSE}
curr <- n.journals.year$Journal.count[-1]
prev <- n.journals.year$Journal.count[1:(length(n.journals.year$Journal.count)-1)]
annualChange.numeric <- c(0, (100 * (curr-prev)/ prev))
annualChange.dichotomous <- ifelse(annualChange.numeric < 0, "Decrease", "Increase")
annualChange.df <- data.frame(annualChange.numeric, annualChange.dichotomous)
annualChange.df$year <- c(1989:2013)

@@

```{r plot02_SmallMultiples, eval=FALSE}
# Remove 2014 & 2015

@@

```{r plot03_AuthorPages, eval=FALSE}

#----------------------------
#Authors
#----------------------------

year.df <- full.df %>%
    filter(attributes == "pubYear") %>%
    select(id = articleID, pubYear = record)

authors.df <- full.df %>%
    filter(attributes == "author") %>%
    select(id = articleID, author = record)

n_authors <- authors.df %>%
    group_by(id) %>%
    summarise(n=n())

n_authors <- n_authors%>% 
    left_join(year.df) %>%
    group_by(pubYear) %>%
    mutate(n = as.numeric(n)) %>%
    summarise(median.n = median(n),
        average.n = mean(n),
        min.n = min(n),
        max.n = max(n),
        std.dev  = sd(n) )

n_authors2 <- n_authors%>% 
   select(median.n, average.n, std.dev) %>%
   rename(Median = median.n, Average = average.n, Standard_Deviation =std.dev)

n_authors2$year <- c(1989:2013)

cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )

n_authors2.melted <- reshape2::melt(n_authors2, id.vars = c("year", "Standard_Deviation"))
n_authors3.melted <- filter(n_authors2.melted, variable == "Average")

plot.author.count <- ggplot(n_authors2.melted, aes(x = year, y = value, group=variable, colour = variable)) + 
    theme_bw() + 
    geom_line() +
    geom_point(data = n_authors3.melted, aes(size = Standard_Deviation), colour = "#e66101", alpha=.60) + 
    #theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    #title = element_text(size = 10)) +  
    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
    scale_y_continuous(limits = c(.75,2.5)) +
    ylab("Number of Authors") +
    xlab("") +
    labs(size = "SD = ") +
    labs(colour = NULL) + 
    scale_colour_manual(values = c("#fdb864", "#e66101")) +
    theme(axis.title.x = element_text(vjust=-0.5), 
          axis.title.y = element_text(vjust=.75), 
          legend.position = "bottom") + 
       theme(title = element_text(size = 10)) +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) +
    theme(legend.text = element_text(size = 8), legend.title = element_text(face="plain"))

n_authors_grouped <- n_authors %>%
    mutate(n = ifelse(n >= 4, 4, n)) %>%
    group_by(pubYear) %>%
    mutate(n.year = n()) %>%
    group_by(pubYear, n) %>%
    summarize(N =  n()) %>%
    group_by(pubYear) %>%
    mutate(N.year.overall = sum(N)) %>%
    mutate(N.percent = (N/N.year.overall)*100)

ggplot(n_authors_grouped, aes(pubYear, N.percent, group = n, colour = as.factor(n))) + geom_line(size = 1.5) + 
    scale_colour_manual(values = cp) +
    labs(colour = "Number of Authors") + 
    ylim(c(0,100)) + 
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75), 
          legend.position = "bottom") +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10))

```{r eval=FALSE}
#----------------------------
#Pages
#----------------------------

cp <- c("#fdb864", "#e66101", "#b2abd2", "#5e3c99" )
pages.tmp <- full.df %>% filter(attributes == "pages")
years.tmp <- full.df %>% filter(attributes == "pubYear")
pages.df <- left_join(pages.tmp, years.tmp, by = "articleID") %>% 
    select(record.y, record.x) %>%
    rename(years = record.y, pages = record.x) %>%
    mutate(pages = as.numeric(pages), years = as.numeric(years)) %>%
    group_by(years) %>%
    summarise(
        Median = median(pages, na.rm=TRUE), 
        Average = mean(pages, na.rm=TRUE),
        Std.Pages = sd(pages, na.rm=TRUE))

pages.df$years <- c(1989:2013)

pages.df.melted <- reshape2::melt(pages.df, id.vars = c("years", "Std.Pages"))

pages.df2.melted <- filter(pages.df.melted, variable == "Average")

page.plot <- ggplot(pages.df.melted, aes(x = years, y = value, group=variable, colour = variable)) + 
    geom_line() +
    geom_point(data = pages.df2.melted, aes(size = Std.Pages), colour = "#5e3c99", alpha = .60) + 
    theme_bw() + 
    theme(title = element_text(size = 10)) +  
    scale_x_continuous(breaks=c(seq(1989, 2013, 4))) +
    ylab("Number of Pages") +
    xlab("") +
    labs(size = "SD = ") +
     labs(colour = NULL) +   
    scale_colour_manual(values = c("#b2abd2", "#5e3c99"))  +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75), 
          legend.position = "bottom") +
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) +
    theme(legend.text = element_text(size = 8), legend.title = element_text(face="plain"))

```{r CAGR comparison, eval=FALSE}

@@

```{r appendix_A_intersection, eval=FALSE}
unique.swHistory <- filter(full.df, attributes == "journal") %>%
    distinct(record)

hodge.swHistory.intersect <- intersect(hodge, unique.swHistory$record)

hodge.swHistory.diff <- setdiff(hodge, unique.swHistory$record)

\newpage

```{r finalArticleListecho=FALSE, comment=NA, eval=FALSE}
#print.data.frame(final.list, row.names=FALSE)
```

\newpage

```{r, eval=FALSE}
grid.arrange(plot.journal.count, plot.article.count, ncol=2)

```
\newpage
```{r fig.height=10, fig.width=7.5, eval=FALSE}
plotSmallMultiples.1

\newpage
```{r fig.height=10, fig.width=7.5, eval=FALSE}
plotSmallMultiples.2

\newpage

```{r eval=FALSE}

grid.arrange(plot.author.count, page.plot, ncol = 2)
```

\newpage

```{r eval=FALSE}
evidence.plot
```
\newpage

```{r eval=FALSE}
stacked.plot
```

\newpage
```{r eval=FALSE}
grid.arrange(journal.evidence.plot, propPlot, 
        ncol=2, nrow=1, widths=c(2, 1), heights=c(1.4, 4))
```

\newpage

# Appendix A

Articles on Hodge and Lacasse (2011) but not in the current study.

```{r appendix_Print, eval=FALSE}
print(sort(hodge.swHistory.diff))
print(fewArticles)
```

>>>>

```{r summarySetUp, eval=TRUE}

#=======================================
# Descriptives
#=======================================

numberArticles <- length(which(full.df$attributes == "article"))

numberJournals <- filter(full.df, attributes == "journal") %>%
  summarise(Unique = n_distinct(record))

unique.swHistory <- filter(full.df, attributes == "journal") %>%
    distinct(record)

hodge.swHistory.intersect <- intersect(hodge.df, unique.swHistory$record)

hodge.swHistory.diff <- setdiff(hodge.df, unique.swHistory$record)

```{r Table 1 Journal Summary, eval=TRUE }
#=======================================
# Table 1. Journal summary 
#=======================================
# Integrate min - max years for each journal
unique.titles <- filter(full.df, attributes == "journal") %>%
  group_by(record) %>%
  mutate(Hodge = ifelse(record %in% hodge.df == TRUE, "Y", "N")) %>%
  summarise(N = n(), Hodge.list = max(Hodge))

```{r Figure 2 Journal Growth, eval = TRUE}
#=======================================
# Journals
#=======================================

@@

figure2 <- ggplot(n.journals.year, aes(record.y, 
    y = Journal.count)) + 
    theme_bw() + 
    theme(axis.text.x = element_text(size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 95)) +
    theme(axis.title.x = element_text(vjust=-0.5), axis.title.y = element_text(vjust=.75)) + 
    geom_line(aes(x = record.y, y = exp.05, colour = "Estimated 5% CAGR"),
        data = n.journals.year,   colour = cp[2], alpha = .80) +
    geom_line(aes(x = record.y, y = exp.04, colour = "Estimated 4% CAGR"), 
        data = n.journals.year,  colour = cp[2], alpha = .80) +
    geom_line(aes(colour = "Observed Growth"), colour = cp[4], size = 1.5) + 
    stat_smooth(method = "lm", se = FALSE, colour = cp[3]) +
    annotate("text", x = 2016.5, y = 60, label = "Observed growth", size = 5) +
    annotate("text", x = 2016.5, y = 70, label = "Linear growth\n (slope=1.9)", size = 5) + 
    annotate("text", x = 2016, y = 76, label = "4% CAGR", size = 5) + 
    annotate("text", x = 2015.5, y = 95, label = "5% CAGR", size = 5) +
    scale_x_continuous(limits = c(1989, 2020), breaks = c(1989, 1993, 1997, 2001, 2005, 2009, 2013)) +
    ggtitle("Figure 2. Observed Versus Estimated Growth of Journals (1989-2013)") + 
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
          panel.border = element_blank(), axis.line = element_line(), 
          axis.text.x = element_text(size = 16), 
          axis.text.y = element_text(size = 16), 
          axis.title.x = element_text(size = 16), 
          axis.title.y = element_text(size = 16)) +
    theme(plot.title = element_text(size = 19))
```

```{r Figure 3 Annual Change, eval=FALSE}
curr <- n.journals.year$Journal.count[-1]
prev <- n.journals.year$Journal.count[1:(length(n.journals.year$Journal.count)-1)]
annualChange.numeric <- c(0, (100 * (curr-prev)/ prev))
annualChange.dichotomous <- ifelse(annualChange.numeric < 0, "Decrease", "Increase")
annualChange.df <- data.frame(annualChange.numeric, annualChange.dichotomous)
annualChange.df$year <- c(1989:2013)

@@

```{r plot02_SmallMultiples, eval=FALSE}
# Remove 2014 & 2015 
n.so <- filter(full.df, attributes == "journal") %>% mutate(title = record) %>% 
  select(-attributes, -record)

@@

```{r Figure 4 CAGR Comparison, eval=FALSE}

@@
